---
title: "PackageExamples"
author: "Rob Donald"
date: "`r format(Sys.time(), '%A %d %B %Y, %H:%M')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
params:
  dataprep: true
header-includes: \usepackage{comment}
---
<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>


# Introduction

This is a .Rmd to provide some examples of using packages I have on GitHub

+ RobsRUtils


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.height=8,fig.width=12)
options(width=1500)
```

# Cross platform operation

Demo the techniques I use to cope with Windows support.

```{r system_setup, echo=FALSE}
os.type<-Sys.info()[1]
if(os.type == 'Windows'){TLC_Root<-'C:/PostDocStuff'}else{TLC_Root<-'/Users/rob/PostDocStuff/teaching/RStuff'}
```

# Conditional markdown text

`r if(!params$dataprep) {"\\begin{comment}"}`
## Libraries
`r if(!params$dataprep) {"\\end{comment}"}`

```{r library_setup,include=params$dataprep}
suppressMessages({suppressWarnings({
    library(dplyr)
    library(RobsRUtils)
})})
```

# Background

First tests are for the MD5 stuff.


```{r}
col1 <- c(1,2,3)
col2 <- c(4,5,6)
status <- c('Pass','Pass','Fail')

df <- data_frame(col1,col2,status)

output.dir <- './data'
dir.create(path = output.dir)

output.filename <- 'Test_Text_File.txt'

full.path <- paste0(output.dir,'/',output.filename)

write.csv(df,file = full.path, row.names = FALSE)
```


We can now examine the file if you want to see the contents

We'll now generate an MD5 file
```{r}
MD5 <- MD5_thisFile(filename = full.path)
MD5
```

We can now check that.

```{r}
VerifyMD5(full.path = full.path, '48F4D3FC25742F3DCFD9752E3AF36D81')
```

```{r}
sessionInfo()
```

